---
title: "tfg"
output: html_document
date: "2023-05-05"
---

EME10. ELENA GALLEGO, VIKTORIYA KROT AND SALMA FERRER. R MARKDOWN. 

Project title: "The determinants of prices for real estate in Barcelona". 
Code for the project. 
```{r}
#Load the necessary libraries
library(tidyverse)
library(dplyr)
library(dygraphs)
library(DT)
library(fivethirtyeight)
library(gt)
library(maps)
library(plotly)
library(threejs)
library(tidyquant)
library(rworldmap)
library(ggmap)
library(leaflet)
library(stringr)
library(highcharter)
library(ggcorrplot)
library(ggplot2)
library(dplyr)
library(tidyr)
library(broom)
library(glmnet)
library(ggstance)
library(lme4)
library(knitr)
library(sf)
library(sjPlot)
```


```{r}
#Read dataset
dataset <- read_delim("/Users/salmaferrer/Desktop/Salma/Universidad/Cuarto/tfg/datatfg.csv", delim=",",locale = locale(decimal_mark=","))
```
```{r}
#Do logarithm transformations
dataset$ln_price <- log(dataset$price)
dataset$ln_square_meters <- log(dataset$square_meters)
```

#EXPLORATORY DATA ANALYSIS

```{r}
#Load the geoJSON files for the mapping
geojson_barris <- file.choose()
geojson_barris <- st_read(geojson_barris)
geojson_district <- file.choose()
geojson_district <- st_read(geojson_district)
```

##Rent price per neighbourhood
```{r}
#Upload dataset for neighbourhood observations
subset_n <- read_delim("/Users/salmaferrer/Desktop/Salma/Universidad/Cuarto/tfg/dataset_barris.csv", delim=",",locale = locale(decimal_mark=","))
```


```{r}
#Merge the neighbourhood dataset with the mapping dataset
barris <- subset_n %>% select(mean_price)
merged <- cbind(geojson_barris, barris) 

ggplot() +
  geom_sf(data = merged, aes(fill = mean_price)) +
  scale_fill_gradient(low = "pink", high = "brown") +
  theme_void()
```

```{r}
ggplot(dataset, aes(x = neighbourhood, y = price)) +
  geom_bar(stat = "identity", fill = "coral3") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  xlab("Neighborhoods") +
  ylab("Rent Prices") +
  ggtitle("Rent Prices by Neighborhood in Barcelona")
```



##Rent price per district
```{r}
#Load district dataset
subset_d <- read_delim("/Users/salmaferrer/Desktop/Salma/Universidad/Cuarto/tfg/dataset_districts.csv", delim=",",locale = locale(decimal_mark=","))
```

```{r}
#Merge district dataset with mapping dataset
districts <- subset_d %>% select(d_mean_price, NOM)
merged_data <- merge(geojson_district, districts, by = "NOM", all.x = TRUE)

ggplot() +
  geom_sf(data = merged_data, aes(fill = d_mean_price)) +
  scale_fill_gradient(low = "pink", high = "brown") +
  theme_void()
```

```{r}
ggplot(dataset, aes(x = price, fill = district)) +
  geom_histogram(binwidth = 100, position = "identity") +
  theme_minimal() +
  xlab("Rent Prices") +
  ylab("Count") +
  ggtitle("Price Distribution by Districts") +
  facet_wrap(~ district, nrow = 5)
```



##Average income per neighbourhood

```{r}
subset_n <- read_delim("/Users/salmaferrer/Desktop/Salma/Universidad/Cuarto/tfg/dataset_barris.csv", delim=",",locale = locale(decimal_mark=","))
```

```{r}
barris_income <- subset_n %>% select(average_disposable_income)
merged <- cbind(geojson_barris, barris_income) 
ggplot() +
  geom_sf(data = merged, aes(fill = average_disposable_income)) +
  scale_fill_gradient(low = "pink", high = "brown") +
  theme_void()
```

##Average income per district

```{r}
subset_d <- read_delim("/Users/salmaferrer/Desktop/Salma/Universidad/Cuarto/tfg/dataset_districts.csv", delim=",",locale = locale(decimal_mark=","))
```

```{r}
district_income <- subset_d %>% select(average_net_income)
merged <- cbind(geojson_district, district_income) 

ggplot() +
  geom_sf(data = merged, aes(fill = average_net_income)) +
  scale_fill_gradient(low = "pink", high = "brown") +
  theme_void()
```

##Temporal accommodations per district
```{r}
subset_d <- read_delim("/Users/salmaferrer/Desktop/Salma/Universidad/Cuarto/tfg/dataset_districts.csv", delim=",",locale = locale(decimal_mark=","))
```

```{r}
district_temp<- subset_d %>% select(d_numb_temp)
merged_temp <- cbind(geojson_district, district_temp) 
ggplot() +
  geom_sf(data = merged_temp, aes(fill = d_numb_temp)) +
  scale_fill_gradient(low = "pink", high = "brown") +
  theme_void()
```

##Temporal accommodations per neighbourhood
```{r}
subset_n <- read_delim("/Users/salmaferrer/Desktop/Salma/Universidad/Cuarto/tfg/dataset_barris.csv", delim=",",locale = locale(decimal_mark=","))
```

```{r}
barris_temp <- subset_n %>% select(n_numb_temp)

merged <- cbind(geojson_barris, barris_temp) 
ggplot() +
  geom_sf(data = merged, aes(fill = n_numb_temp)) +
  scale_fill_gradient(low = "pink", high = "brown") +
  theme_void()
```



##Unemployment per district
```{r}
district_unemp <- subset_d %>% select(d_unemployment_relative)

merged <- cbind(geojson_district, district_unemp) 
ggplot() +
  geom_sf(data = merged, aes(fill = d_unemployment_relative)) +
  scale_fill_gradient(low = "pink", high = "brown") +
  theme_void()
```

##Unemployment per neighbourhood
```{r}
barris_unemp <- subset_n %>% select(n_unemployment_relative)

merged <- cbind(geojson_barris, barris_unemp) 
ggplot() +
  geom_sf(data = merged, aes(fill = n_unemployment_relative)) +
  scale_fill_gradient(low = "pink", high = "brown") +
  theme_void()
```


#REGRESSION MODELS
##Regression using real estate characteristics

```{r}
lmfit6 <- lm(ln_price ~ temporal + furnished + district + bedrooms + bathrooms + ln_square_meters + elevator + balcony + heating + metro + energy_ratings + real_estate_agency, data = dataset)
summary(lmfit6)
```


```{r}
#Present the results in a table
tab_model(lmfit6, 
          transform = NULL, auto.label = FALSE, 
          dv.labels = c("Linear regression housing characteristics"))
```


##Regression using real estate and neighbourhood characteristics

```{r}
lmfit7 <- lm(ln_price~  n_metro_stations + n_pop + n_disposable_income + n_unemployment + n_green_areas + n_mean_n02pp + n_spanish + n_mean_age_flats + temporal + furnished + district + bedrooms + bathrooms + ln_square_meters + elevator + balcony + heating + metro + energy_ratings + real_estate_agency, data= dataset)

summary(lmfit7)
```

```{r}
tab_model(lmfit7, 
          transform = NULL, auto.label = FALSE, 
          dv.labels = c("Adding neighbourhood ch."))
```



##Regression using real estate and district characteristics

```{r}
lmfit8 <- lm(ln_price ~ d_pop + d_avgmonth_income + d_spanish + d_noise_complaints + d_mean_n02pp + d_poverty_risk+ d_metro_stations + temporal + metro + furnished + bedrooms + bathrooms + ln_square_meters + elevator + balcony + heating + energy_ratings + real_estate_agency, data= dataset)

summary(lmfit8)
```


```{r}
tab_model(lmfit8, 
          transform = NULL, auto.label = FALSE, 
          dv.labels = c("Adding district ch."))
```


#APPENDIX
##Regression using real estate characteristics, for each district

```{r}
#Create subsets for each district
ciutatvella_data <- subset(dataset, district == "Ciudad Veja")
eixample_data <- subset(dataset, district == "Ensanche")
santsmontjuic_data <- subset(dataset, district == "Sants-Montjuïc")
lescorts_data <- subset(dataset, district == "Les Corts ")
sarriastgervasi_data <- subset(dataset, district == "Sarriá-San Gervasiol ")
gracia_data<- subset(dataset, district == "Gracia")
horta_data<- subset(dataset, district == "Horta-Guinardó")
noubarris_data <- subset(dataset, district == "Nou Barris")
santandreu_data<- subset(dataset, district == "San Andrés")
santmarti_data<- subset(dataset, district == "San Martín ")

```


```{r}
#Hedonic pricing regressions for each district
model_ciutatvella <- lm(ln_price ~ temporal + furnished + bedrooms + bathrooms + ln_square_meters + elevator + balcony + heating + metro + energy_ratings + real_estate_agency, data = ciutatvella_data)

model_eixample <- lm(ln_price ~ temporal + furnished + bedrooms + bathrooms + ln_square_meters + elevator + balcony + heating + metro + energy_ratings + real_estate_agency, data = eixample_data)

model_santsmontjuic <- lm(ln_price ~ temporal + furnished + bedrooms + bathrooms + ln_square_meters + elevator + balcony + heating + metro + energy_ratings + real_estate_agency, data = santsmontjuic_data)

model_lescorts <- lm(ln_price ~ temporal + furnished + bedrooms + bathrooms + ln_square_meters + elevator + balcony + heating + metro + energy_ratings + real_estate_agency, data = lescorts_data)

model_sarriastgervasi <- lm(ln_price ~ temporal + furnished + bedrooms + bathrooms + ln_square_meters + elevator + balcony + heating + metro + energy_ratings + real_estate_agency, data = sarriastgervasi_data)

model_gracia <- lm(ln_price ~ temporal + furnished + bedrooms + bathrooms + ln_square_meters + elevator + balcony + heating + metro + energy_ratings + real_estate_agency, data = gracia_data)

model_horta <- lm(ln_price ~ temporal + furnished + bedrooms + bathrooms + ln_square_meters + elevator + balcony + heating + metro + energy_ratings + real_estate_agency, data = horta_data)

model_noubarris <- lm(ln_price ~ temporal + furnished + bedrooms + bathrooms + ln_square_meters + elevator + balcony + heating + metro + energy_ratings + real_estate_agency, data = noubarris_data)

model_santandreu <- lm(ln_price ~ temporal + furnished + bedrooms + bathrooms + ln_square_meters + elevator + balcony + heating + metro + energy_ratings + real_estate_agency, data = santandreu_data)

model_santmarti <- lm(ln_price ~ temporal + furnished  + bedrooms + bathrooms + ln_square_meters + elevator + balcony + heating + metro + energy_ratings + real_estate_agency, data = santmarti_data)
```


```{r}
#Summary table for the regression models by district
model_list <- list(model_ciutatvella, model_eixample, model_santsmontjuic, model_lescorts, model_sarriastgervasi, model_gracia, model_horta, model_noubarris, model_santandreu, model_santmarti)

model_labels <- c("Ciutat Vella", "Eixample", "Sants-Montjuïc", "Les Corts", "Sarrià-Sant Gervasi", "Gracia", "Horta-Guinardó", "Nou Barris", "Sant Andreu", "Sant Martí")
tab_model(
  models = model_list,
  transform = NULL,
  auto.label = FALSE,
  dv.labels = model_labels
)
```






